---
title: "Weight of Fish"
author: "Teresa Juan"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

```{r}
All_Fish <- read.csv(file = "Fish.csv")
```


```{r}
Perch <- filter(All_Fish, Species=="Perch")
```

```{r}
Perch <- select(Perch, -Species)
```

# Predicting Fish Weight

## Perch

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models
best model for Perch is height and width

### Best Two regressor model 
The best two regressor model that adjustedRsquare gave us is height and width. Landing on subset size on 2 and on Y linear 0.9400

## Pike

```{r}
Pike <- filter(All_Fish, Species=="Pike")
```

```{r}
Pike <- select(Pike, -Species)
```


```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Models
The best models are lenght1, lenght2, lenght3, height, width, because its has the highest adjustedRsquare, adjusted square is on 0.9880, its bigger and higher then everyone else.

### Best Two regressor model
The best two regressor model are length1 and length3, after adjusted R square tested out all these levels, it gave us these two best.

## Roach


```{r}
Roach <- filter(All_Fish, Species=="Roach")
```

```{r}
Roach <- select(Roach, -Species)
```

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best  models that adjustedRsuqare gave us is length3, and width. looking at the date L3 and lenght is on the topof all the other models with being at almost 0.850

### Best Two regressor model

The best two regressor models that adjuster R square trew us is lenght3 and width. being that it landed on subset size is on 2 and adjusted R square is on 0.850.

## Final Summary Statements

