---
title: "Weight of Fish"
author: "Teresa Juan"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

```{r}
All_Fish <- read.csv(file = "Fish.csv")
```


```{r}
Perch <- filter(All_Fish, Species=="Perch")
```

```{r}
Perch <- select(Perch, -Species)
```

# Predicting Fish Weight

## Perch

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models
best model for Perch is height and width

### Best Two regressor model 
The best two regressor model that adjustedRsquare gave us is height and width. Landing on subset size on 2 and on Y linear 0.9400

## Pike

```{r}
Pike <- filter(All_Fish, Species=="Pike")
```

```{r}
Pike <- select(Pike, -Species)
```


```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Models
The best models are lenght1, lenght2, lenght3, height, width, because its has the highest adjustedRsquare, adjusted square is on 0.9880, its bigger and higher then everyone else.

### Best Two regressor model
The best two regressor model are length1 and length3, after adjusted R square tested out all these levels, it gave us these two best.

## Roach


```{r}
Roach <- filter(All_Fish, Species=="Roach")
```

```{r}
Roach <- select(Roach, -Species)
```

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best  models that AdjustedR^2 gave us is length3, and width. looking at the date L3 and lenght is on the topof all the other models with being at almost 0.850

### Best Two regressor model

The best two regressor models that AdjustedR^2 threw us is lenght3 and width. being that it landed on subset size is on 2 and adjusted R square is on 0.850.

## Final Summary Statements

In conclusion to figure out the best regression model to predict the weight of the 3 types of fish Perch, pike, and Roach, we used the multiple regression data.In order for us to obtain the results for each individual fish we had to pull them aside from all fishes. First we filled them in to their group to get the variable witch is 6 and then we selected them from the group to obtain the numerical data. Once we had that we ran the multiple regression where AdjustedR^2 gave us the best model, and the best two models for each individual fish. When AdjustedR^2 is running the date, it runs them using each level from weight lenght1, length2 length3, height, and width. From that it chooses which Scores the highest and giving us our model, the higher the better it is. Fore Perch height and weight scored highest,From the best two models subset size set on 2, AdjustedR^2 gave us 0.9400.Fore Pike we got the best model that landed the hightest is L1-L2-L3-H-W.And the best two models 2 subset sise set on 2 gave us  L-1-L-3 and adjustedR^2 on 0.965. For Roach the best model is L3-W, And the two best model is  L3-W subset size set on 2 and AdjustedR^2 on .850.